### 2016-08-10 Engine.tex
继续node merge部分(完成)

The verification module we have just built is based on a big single
AMT which is constructed from the whole pattern set. Actually, we can
divide the big AMT into small ones and enable each verifying procedure
to refer to only one small AMT, by which the time for verifying can be
reduced. The division is based on the following observations.

As stated in Section \ref{sec:filter}, the filtering is based on the
last $k$-symbol block of the substring in the sliding window. In
particular, for a position $i$ of the text $T$, if some pattern $p_j$
starts at $i$, there must be
$Hash[T[i+lss-k,k]] = Hash[p_j[lss-k+1,k]]$ (we call
$Hash[p_j[lss-k+1,k]]$ the \emph{signature} of $p_j$). This means that
we can group the patterns according to their signatures: patterns with
the same signature are grouped together to form a sub-pattern-set, and
for each sub-pattern-set we build a (small) AMT. In addition, an index
table is adopted to allow the corresponding AMT be retrieved in $O(1)$
time by its signature. Now, the verification module is made up of an
index table as well as several small AMTs.

@@

The nodes in a path of AMT, each of which has only one key, can be
merged into one node. This technique can reduce both time and space
efficiency of the verification module. To illustrate this, consider
the pattern set $P=\{p_1=e^6u^5sscc,\, p_2=e^6u^5,\, p_3=e^6\}$ and
its corresponding AMT constructed by Algorithm 1. As shown in Fig (a),
the built AMT has three nodes, and each contains only one key. In a
typical x86\_64 architecture, this implementation of AMT roughly takes
55 bytes of memory: 15 bytes for the keys, 16 bytes for the child
pointers and 24 bytes for the pointers to the matching
functions. However, if we combine the three keys into one string, the
three nodes can be merged into one node (Fig (b)), as a result, the
child pointers are no longer needed and the number of function
pointers is reduced from three to one. The merged node is another type
of tree node in addition to the types we have introduced in Section
\ref{subsec:nodes}.

The only problem is to distinguish among the keys after they are
concatenated, to address this issues, an \emph{length array} is used
to store the length of each key, where each array element takes only
one byte (using the \emph{unsigned char} type). From the length of
each key, we can split the original keys out, and searching the target
string in the merged node can be trivial.

In general, after node merging, the AMT contains only one merged node
which takes 26 bytes (15 bytes for the keys, 3 bytes for the length
array, and 8 bytes for the matching function pointer), thus, 29 bytes
are saved comparing with the original AMT.

>>>>

The verification module we have just built is based on a big single
AMT which is constructed from the whole pattern set. In fact, we can
divide the big AMT into small ones and enable each verifying procedure
to refer to only one small AMT, by which the time for verifying can be
reduced. The division is based on the following observations.

As stated in Section \ref{sec:filter}, the filtering is based on the
last $k$-symbol block of the substring in the sliding window. In
particular, for a position $i$ of the text $T$, if some pattern $p_j$
starts at $i$, there must be
$Hash[T[i+lss-k,k]] = Hash[p_j[lss-k+1,k]]$ (we call
$Hash[p_j[lss-k+1,k]]$ the \emph{signature} of $p_j$). This means that
we can group the patterns according to their signatures: patterns with
the same signature are grouped and form a sub-pattern-set, and for
each sub-pattern-set we build a (small) AMT. In addition, an index
table is adopted to allow the corresponding AMT be retrieved in $O(1)$
time by its signature. Now, the verification module consists of an
index table as well as several small AMTs.

@@

Similar to the ``path compression'' technique widely used in trie-like
structures, the nodes in a path of AMT, each of which has only one
key, can be merged into one node. This technique can improve both time
and space efficiency of AMT. To illustrate this, consider the pattern
set $P=\{p_1=e^6u^5sscc,\; p_2=e^6u^5,\; p_3=e^6\}$ and its
corresponding AMT constructed by Algorithm 1. As shown in Fig (a), the
built AMT has three nodes, and each contains only one key. In a
typical x86\_64 architecture, this implementation of AMT roughly takes
55 bytes of memory: 15 bytes for the keys, 16 bytes for the child
pointers and 24 bytes for the pointers to the matching
functions. However, if we combine the three keys into one string,
these three nodes can be merged into one node (Fig (b)), as a result,
the child pointers are no longer needed and the number of function
pointers is reduced from three to one. The merged node is another type
of tree node in addition to the types we have introduced in Section
\ref{subsec:nodes}.

For the merged node, the only problem is how to distinguish among the
keys after they are concatenated, to address this issues, a
\emph{length array} is used to store the length of each key, where
each array element takes only one byte (using the \emph{unsigned char}
type). Through the length of each key, we can split the original keys
out, and searching the target string in the merged node can be
trivial.

In general, after node merging, the AMT contains only one merged node
which takes 26 bytes (15 bytes for the keys, 3 bytes for the length
array, and 8 bytes for the matching function pointer), thus, 29 bytes
are saved comparing with the original AMT. In addition, only one
random access to the memory is needed to get the merged node (the
original AMT needs three random memory accesses to get all its nodes),
thus, the cache can be fully used to improve the performance.
